Automatic Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-05 paper/paper_new.tex
Updates from Overleaf

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{comment}
\usepackage{todonotes}
\usepackage{wrapfig}
\usepackage{hyperref}
\usepackage{xurl}
\usepackage{booktabs}
\usepackage{float}
\usepackage[noadjust]{cite}

@@

Our work stands apart from previous work in that we are
addressing a different need. Lack of metadata is impeding scientific studies.
Our focus and motivation are different.
Effectively doing the computational pre-processing
that will enable further downstream analyses.

We are applying a variety of machine learning, image processing and
image informatics techniques to extract critical properties from the
images.  The properties will allow follow-on studies to identify
the specific images needed for a particular analysis, ensuring that
the specimen images meet both scientific and technical requirements.

@@

Digitized specimen collections offer numerous outstanding opportunities
for new scientific studies and discoveries.
%I think we can go from the above, statement, directly to the paragraph that starts with "Given the many..." Then, specifically state the goal of this paper is to XXXX address the need, or the goal is to investigate, test, (pick your verb) an approach automatically generating metadata, combining off-the-shelf software and custom written, or is it simply test off-the-shelf software, and later the realization that customization happens.
The amount of data is immense, with image collections containing 10,000's
of entries. These discoveries will only be possible
with computational techniques that can process this vast amount of data.

These image-based computational techniques are hampered by both poor
image quality and the lack of high-quality and pertinent metadata
associated with collections.

For example, a study may require images that contain only one fish with a
given level of lighting and contrast. Additionally, performing quantitative
investiations into the morphology of the specimens requires knowing
the physical scale of the images, i.e.~pixels/inch.

Given the many thousands of images that have and will be acquired of
biological specimens, it is infeasible to generate the needed metadata
via manual, i.e. via human input, methods.  It is critical to deploy
computational techniques that will automate the process of generating
the metatdata that is essential for downstream analyses and studies.

In order to address the need for fish specimen image metadata that can
support scientific investigations we have begun the deployment of
both off-the-shelf and custom-written software that automatically
generates a variety of metadata from a publicly-available biological
image repository.  The types of metadata being produced are related
to image quality, content and scale, and should provide the information
necessary for advanced quantitative studies of the digitized specimens.

The automated metadata generation methods for our project were developed
to work on a specific set of images, the INHS\ Fish
Collection~\cite{INHS}.  Most of these images have been configured,
produced and acquired with a standard procedure.  The images used for
our study contain one fish placed on a bright, white background and
contain an information tag and the same ruler.  See
Figure \ref{fig:teaser} for two example images from the collection.
While training and focusing our system on images with very similar
compositions and visual properties may limit its immediate applicability,
our efforts do demonstrate the potential that machine learning and
image informatics techniques have for automatically generating metadata
for biological specimen image collections.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.49\linewidth]{images/wrong_side_orig}
  \includegraphics[width=0.49\linewidth]{images/wrong_side1}
  \caption{A fish for which a splotch on its tail fin was labeled the most likely eye.}
  \label{fig:wrong_eye}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.7\linewidth]{images/curved1}
  \caption{An example of a heavily curved specimen.}
  \label{fig:curvedFish}
\end{figure}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{comment}
%\usepackage{todonotes}
\usepackage{wrapfig}
\usepackage{hyperref}
\usepackage{xurl}
\usepackage{booktabs}
\usepackage{float}
\usepackage[noadjust]{cite}

@@

Our work stands apart from previous work in that we are
addressing a different need. Lack of metadata is impeding scientific studies.
Our focus and motivation are different.
Effectively doing the computational pre-processing
that will enable further downstream analyses.
%RE: paragraph directly above, DAVE/JOEL - thinking we should we shift message a little bit to something like, e.g., The research reviewed above demonstrates image features extraction; although researchers have not applied these approaches the rich and extensive collections of digitized specimens accessible in open repositories. Our research addresses this need by applying machine learning and informatics techniques to extract key metadata properties from the images, and, further computing higher-level metadata based on these initial results. Our goals and objectives our presented below.

%I think this paragraph could be deleted then, or moves elsewhere, we say this a lot already: We are applying a variety of machine learning, image processing and image informatics techniques to extract key metadata properties from the images. These properties a critical for selecting high-quality, usable digitized specimens for further computational analysis, and and ensuring that the specimen images meet both scientific and technical requirements.

@@

Digitized specimen accessible in open access repositories provide a rich, extensive data source machine-learning and scientific discovery, however, these resources remain largely untapped due image quality and metadata limitations. We are addressing this need by combining machine-learning and image informatics technqiues. The overall goal of our

%Following is original Goals/objectives text: The amount of data is immense, with image collections containing 10,000's of entries. These discoveries will only be possible with computational techniques that can process this vast amount of data.

%These image-based computational techniques are hampered by both poor image quality and the lack of high-quality and pertinent metadata associated with collections.

%For example, a study may require images that contain only one fish with a given level of lighting and contrast. Additionally, performing quantitative investiations into the morphology of the specimens requires knowing the physical scale of the images, i.e.~pixels/inch.

%Given the many thousands of images that have and will be acquired of biological specimens, it is infeasible to generate the needed metadata via manual, i.e. via human input, methods.  It is critical to deploy computational techniques that will automate the process of generating the metatdata that is essential for downstream analyses and studies.

%In order to address the need for fish specimen image metadata that can support scientific investigations we have begun the deployment of both off-the-shelf and custom-written software that automatically generates a variety of metadata from a publicly-available biological image repository.  The types of metadata being produced are related to image quality, content and scale, and should provide the information necessary for advanced quantitative studies of the digitized specimens.

%The automated metadata generation methods for our project were developed to work on a specific set of images, the INHS\ Fish Collection~\cite{INHS}.  Most of these images have been configured, produced and acquired with a standard procedure.  The images used for our study contain one fish placed on a bright, white background and contain an information tag and the same ruler.  See Figure \ref{fig:teaser} for two example images from the collection. While training and focusing our system on images with very similar compositions and visual properties may limit its immediate applicability, our efforts do demonstrate the potential that machine learning and image informatics techniques have for automatically generating metadata for biological specimen image collections.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/wrong_side_orig}
  \includegraphics[width=0.49\linewidth]{images/wrong_side1}
  \caption{A fish for which a splotch on its tail fin was labeled the most likely eye.}
  \label{fig:wrong_eye}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\linewidth]{images/curved1}
  \caption{An example of a heavily curved specimen.}
  \label{fig:curvedFish}
\end{figure}
